%% start of file `cv_pl_dobroslaw_zybort.tex'.
%% Copyright 2013-2016 Dobrosław Żybort (dobroslaw.zybort@gmail.com).


\documentclass[11pt,a4paper,sans,polish]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\usepackage[T1]{fontenc}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=1.5cm,bmargin=2cm,lmargin=0.07\paperwidth,rmargin=0.07\paperwidth,footskip=1cm}

\usepackage{fancyhdr}
\pagestyle{fancy}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{babel}
\usepackage{setspace}
\onehalfspacing
\ifx\hypersetup\undefined
  \AtBeginDocument{%
    \hypersetup{unicode=true,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=false,
 pdfauthor={Dobrosław Żybort},
 pdfkeywords={Dobrosław Żybort,Curriculum Vitae,Resume},
 pdfpagelayout=OneColumn, pdfnewwindow=true, pdfstartview=XYZ, plainpages=false}
  }
\else
  \hypersetup{unicode=true,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=false,
 pdfauthor={Dobrosław Żybort},
 pdfkeywords={Dobrosław Żybort,Curriculum Vitae,Resume},
 pdfpagelayout=OneColumn, pdfnewwindow=true, pdfstartview=XYZ, plainpages=false}
\fi

% moderncv themes
\moderncvstyle{classic}                      % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                         % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}   % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8x]{inputenc}                 % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
% \usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{2.7cm}           % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}     % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\firstname{Dobrosław}
\familyname{Żybort}
\title{Curriculum Vit\ae{}}
% \address{Broniewskiego 26a/m.12}{93-142 Łódź}{Polska}
\mobile{791 673 189}
% \phone{+2~(345)~678~901}
% \fax{+3~(456)~789~012}
\email{dobroslaw.zybort@gmail.com}
\homepage{github.com/matrixik}
% \extrainfo{additional information}
% \photo[64pt][0.4pt]{picture}               % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
% \quote{Some quote}

% Wyrażenie zgody na przetwarzanie danych osobowych
\fancypagestyle{zgoda}{%
  \fancyhf{}
  \renewcommand\headrulewidth{0pt}
  \fancyfoot[R]{\fontsize{9}{11} \selectfont Wyrażam zgodę na przetwarzanie moich danych osobowych w celach rekrutacji, zgodnie z Ustawą z dn. 29 sierpnia 1997 r. o ochronie danych osobowych (Dz. U. z 2002 r. Nr 101, poz. 926 z późniejszymi zmianami).}
}


%% Styl

\urlstyle{same}

% Wielkość czcionki
% \renewcommand*{\namefont}{\fontsize{34}{36}\mdseries\upshape}
% \renewcommand*{\titlefont}{\LARGE\mdseries\slshape}
% \renewcommand*{\addressfont}{\small\mdseries\slshape}
% \renewcommand*{\quotefont}{\large\slshape}
% \renewcommand*{\sectionfont}{\Large\mdseries\upshape}
% \renewcommand*{\subsectionfont}{\large\mdseries\upshape}
% \renewcommand*{\hintfont}{}

\renewcommand*{\sectionfont}{\fontsize{14}{16} \mdseries\upshape}
\renewcommand*{\subsectionfont}{\fontsize{14}{16} \mdseries\upshape}

% Wygląd poziomej linii
%\renewcommand*{\section}[1]{%
%  \par\addvspace{1.5ex}%
%  \phantomsection{}% reset the anchor for hyperrefs
%  \addcontentsline{toc}{section}{#1}%
%  \parbox[t]{\hintscolumnwidth}{\strut\raggedleft\raisebox{\baseletterheight}{\color{color1}\rule{\hintscolumnwidth}{0.60ex}}}%
%  \hspace{\separatorcolumnwidth}%
%  \parbox[t]{\maincolumnwidth}{\strut\sectionstyle{#1}}}%
%  \par\nobreak\addvspace{1ex}\@afterheading}% to avoid a pagebreak after the heading

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-0.8cm}


\section{Doświadczenie zawodowe}

\cventry{\small2015-10 -- obecnie}
	{Ericpol Sp. z o.o.}{}{}
	{Software Developer}
	{Trouble Reports Work Group (C++)}

\cventry{\small2015-01 -- 2015-10}
	{Ericpol Sp. z o.o.}{}{}
	{Scrum Master / Software Developer}
	{Flow team, usuwanie przeszkód programistycznych, Trouble Reports Work Group (C++)}

\cventry{\small2013-07 -- 2014-12}
	{Ericpol Sp. z o.o.}{}{}
	{Scrum Master / Junior Software Developer}
	{Flow team, usuwanie przeszkód programistycznych (C++)}

\cventry{\small2008-07 -- 2009-01}
	{Tekka Sp. z o.o.}{}{}
	{Tester oprogramowania}
	{Testowanie oraz tworzenie dokumentacji dla systemu do zarządzania
	zleceniami w firmie logistycznej}


\section{Projekty prywatne}

\cventry{\small2012-12 -- obecnie}
	{slug, oauth2, ListDict i inne}{open source}{}
	{\url{https://github.com/gosimple}}
	{Biblioteki napisane w języku programowania Go}

\cventry{\small2012-07 -- 2015-11}
	{Wordpress autoposter}{projekt prywatny}{}
	{}
	{Web scraper oraz bot automatyzujący wysyłanie postów na platformę Wordpress,
		administracja 14 blogów i 4 VPS-ów, tech: Go, Python, MySQL, SQLite, Amazon S3}

\cventry{\small2009 -- obecnie}
	{Betfair Watcher, PastebinGo i inne}{open source}{}
	{\url{https://bitbucket.org/matrixik}}
	{Napisane w języku Python i Go boty, strony internetowe oraz programy użytkowe}


\section{Wykształcenie}

\cventry{\small2005 -- 2013}{Wydział Elektrotechniki, Elektroniki, Informatyki
i Automatyki}{Politechnika Łódzka}{Łódź}{Polska}{}
\vspace{-0.2cm}

\cvitem{Specjalność}{\textbf{Bazy Danych i Systemy Ekspertowe}}


\section{Umiejętności}

\cvitemwithcomment
	{Język angielski}
	{Bardzo dobry}{Znajomość terminologii technicznej}

\cvitemwithcomment
	{Języki prog.}
	{Go, Python, C++}{gorilla, goquery, python wordpress xmlrpc, PIL, requests, tinyxml2}

\cvitemwithcomment
	{Bazy danych}
	{SQLite, MySQL}{}

\cvitemwithcomment
	{Web}
	{HTML, CSS}{}

\cvitemwithcomment
	{Inne}
	{Linux Debian, Gerrit, RSARTE \small{(Eclipse + UML)}, LiteIDE, Git, ClearCase, Scrum, Amazon S3}{}


\vspace{0.5cm}

\begin{cvcolumns}
	\cvcolumn[0.7]{Zdolności i certyfikaty}{
		\begin{itemize}
			\item Zarządzenie 8 osobowym zespołem
			\item Bezpośrednia współpraca z zagranicznym klientem
			\item Professional Scrum Master I (PSM I)
			\item Prawo jazdy kat. B
		\end{itemize}}
	\cvcolumn{Zainteresowania}{
		\begin{itemize}
			\item Ludzkie ciało
			\item Technologie jutra
			\item Wycieczki piesze
		\end{itemize}}
\end{cvcolumns}


\thispagestyle{zgoda}

\end{document}
